A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-14 method.tex
fixed typo
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@617 ccdd05d5-56c1-461a-bf98-85f6876523b4

This presents a dilemma: it seems that low latency detection using the \textsc{fir} implementation is prohibitively expensive, whereas computational cheap detection with the \textsc{fft} method comes with minutes to hours of latency.

>>>>

This presents a dilemma: it seems that low latency detection using the \textsc{fir} implementation is prohibitively expensive, whereas computationally cheap detection with the \textsc{fft} method comes with minutes to hours of latency.
